Figures

### 2018-10-02 manuscript/figures.Rmd
fix captions and make paths

```{r fig.cap="Figure 1: Counties that overlap lake watersheds with high agricultural land-use cover that have water quality data in LAGOS.", echo = FALSE, fig.width = 1, out.height = "4in"}
knitr::include_graphics("../figures/01_county_extent.pdf")
```

>>>>

```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 1995 and 2005.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/01_county_extent-1.pdf")
```
